Assessing primitives performance\\ on multi-stage execution

### 2018-05-08 paper.tex
move forward in sec 3

  Can be changed like Smalltalk code (No C compilation whatsoever). Readability. Only impl without VM recompilation.

Baseline performance is not that great.

Number of implementations to maintain: 1, 2 or 3: same implem for primitive in C and fall back code in Smalltalk, relatively easy to read/code.
recompilation. 
changing the prim => changing all clients (VM compil from Pharo or Squeak different results
Performance: cross file inlining not possible by default. (InterpreterProxy indirection)
Control on generated code => difference LLVM/GCC
 Pure C performance (no interpreter proxy).
 no C-St jump. Control over the outcome (reliable performance)
 costly jumps between Smalltalk and C runtime (trampolines), need to recompile vm sources, little control over outcome (c compilers 
 need to recompile vm sources (trampolines), code readability

@@

\cba{expliquer tableau comparatif}

>>>>

 - Requires recompilation of VM or plugin
 - Implementation language familiar to client dev
 - Implementation language familiar to vm dev
 - readability: number of lines of code ? 
 - Number of impl to maintain 1,2,3 or more if multiple clients.
 - Performance: stack switch, C performacne, cross file inlining, (InterpreterProxy indirection)
 - Control on generated code, diff llvm gcc

@@

\cba{Sophie on va se faire tuer, hacher menu et être donné en pature à un élevage de porcs avec ton tableau: des termes comme maintenance c'est bcp trop subjectif. 
Je pense il faut changer sur ce que j'ai mis plus haut qui est beaucoup plus objectif: number of impl to maintain pour maintenance par ex,
readability il faut des criteres concrets comme nombre de lignes meme si ca veut rien dire, tout le monde utilise ce critere.}

\cba{Probleme avec le tableau: Je lis + comme positif, - comme negatif. La Execution time je vois +++ au plus lent, c'est pas clair. X c'est interpreté par les anglosaxons comme NON, pour oui ils veulent le truc qui ressemble à un V}
